\vspace{-0.25em}\thetitle

### 2009-07-23 paper.tex
...

To see the linear structure of these representation matrices, we apply one of the most powerful tools of linear algebra:
the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix, factoring it into a product of three real matrices:
\begin{align}
  X = U\!S\trans{V}.
\end{align}
$U$ and $V$ are orthogonal and $S$ is diagonal, with entries of nonincreasing nonnegative value.
Among the useful properties of this factorization, is that the first $k$ columns of $U\!S$ are an optimal $k$-dimensional reduced model of $X$.\,\svdnote
This property allows us to visualize the structure of $X$ using initial columns of $U\!S$.
However, we are interested only interested in direction since
vectors differing only by magnitude lie in the same one-dimensional subspace.
To visualize direction while eliminating distance, we project all data points onto the unit-sum hyperplane through the origin.\projectionnote

@@

>>>>

To see the linear structure of these representation matrices, we apply one of the most powerful tools of linear algebra:
the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix, factoring it into a product of three real matrices:
\begin{align}
  X = U\!S\trans{V}.
\end{align}
$U$ and $V$ are orthogonal and $S$ is diagonal, with entries of nonincreasing nonnegative value.
Among the useful properties of this factorization, is that the first $k$ columns of $U\!S$ are an optimal $k$-dimensional reduced model of $X$.\svdnote
This property allows us to visualize the structure of $X$ using initial columns of $U\!S$.
However, we are interested only interested in direction since
vectors differing only by magnitude lie in the same one-dimensional subspace.
To visualize direction while eliminating distance, we project all data points onto the unit-sum hyperplane through the origin.\projectionnote

@@

The presence of linear structure in the matrix representations of several independent traffic traces immediately raises two significant questions.
The more philosophical question is \emph{Why does this linear structure exist?}
The more practical question is \emph{How can we exploit this structure?}
Neither question can be answered fully in a single paper.
In what follows, we provide some insight into the first question, and use that insight to predict the behavior of individual flows from the observation of only a few initial packets.

\vfill
\break
